S2 pioneer factor MS

### 2022-09-13 manuscript/manuscript.Rmd
fix gene models in browser tracks in fig 1

# Results

>>>>

# Results
## Ectopic pioneer factors bind and open closed chromatin

## Chromatin opening correlates with transcriptional activation

## Twist binds closed chromatin extensively and opens chromatin at some sites

## Motif content distinguishes chromatin opening by Twist from Zelda and Grainy head

## Ectopic transcription factors bind nonspecifically to active chromatin
